
---
title: "RobotName: CloseBackBB"
output: html_document
---

Version: 91.1

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##this code takes files from TV and process them to create sumamry results comparable among optimizations. This is an improve version f the ones sued in scalper and loaded, which were for leaving positions open until profiting (Martingales) and closing positions, respectively. This version handles both types...by looking at the consequetive entries until reaching profit.
## this versoin assume positions are closed when at a lost.

##########################################################################################
#THIS IS THE ONLY THING TO CHANGE
RobotName="CloseBackBB" # TTTLoadedV1" #ScalperV3 LoadedV1  TTTLoadedV1 Karol Killerzones   BlaiKelt
OptimizationNum= "08"


NameOptimization=paste0(RobotName, "_", OptimizationNum)
Path=paste0("C:/Users/Camilo/Downloads/", NameOptimization,"/",NameOptimization,"/")

###########################################################################################



library(data.table)
library(dplyr)
library(splitstackshape)
library(plotly)
library(tidyr)
library(knitr)
library(ggpubr)

Pairs=c("AUDUSD", "EURGBP", "EURJPY", "EURUSD", "GBPJPY", "GBPUSD", "NZDUSD", "USDCAD", "USDCHF",  "USDJPY", "XAUUSD")
StartingBalance=30000  #amount of initial capital
MinMoneyEntry=1000     #Minimum amount of moey allowed to enter..$1,000 is the least we can invest
MinActive=0.2          #number of entries per day set to 0.2..meaning it will be active atleast 20% of a year...or it will enter at least once a week
GainAtTarget=30        #amount of money at 1% profit per day.. 1% of $30,000
DesireMaxDD=10          # Maximum prcent DD allowed to select parameters
MaxDesDayProf=1         #percentdesired dayliy profit
#get list of files in folder
    ListEntries=data.frame(FileName=list.files(Path))

#process The files with the list of entries...select files with X number of chanrecterS in their name and that the first two letters are A and Zero. (common all all files with entries)
    ListEntries$Letters=nchar(ListEntries$FileName)
    EntryFiles=ListEntries %>% filter(Letters==10)
    EntryFiles$A0=substring(EntryFiles$FileName,1,2)
    EntryFiles=EntryFiles %>% filter(A0=="A0")

    
    
    
#############################################################################
#############--------REsults from list of entries-----------#################
#############################################################################
    
    
    
#calcualte the maximum drowdown of all position open at a given time
Summary=data.frame()
for (FileI in EntryFiles$FileName){
      FileIData=read.csv(paste0(Path,FileI))  
      
      
      colnames(FileIData)[13]="MoneyDD"
      colnames(FileIData)[4]="Date"
      colnames(FileIData)[9]="CumProf"

      FileIData <- FileIData[complete.cases(FileIData[ , c("MoneyDD")]), ]
      
      #find out number of days...time difference between first time entry and when the last exit occured
        #Date last entry
            LastExit=FileIData$Date[1]
            LastExit= strptime(LastExit, format = "%Y-%m-%d %H:%M")
            if (is.na(LastExit)==TRUE){
              LastExit=FileIData$Date[1]
              LastExit= strptime(LastExit, format = "%m/%d/%Y %H:%M")
            }
          
        #Date FIrst entry
            FirstEntry=FileIData$Date[nrow(FileIData)]
            FirstEntry= strptime(FirstEntry, format = "%Y-%m-%d %H:%M")
              if (is.na(FirstEntry)==TRUE){
                FirstEntry=FileIData$Date[nrow(FileIData)]
                FirstEntry= strptime(FirstEntry, format = "%m/%d/%Y %H:%M")
              }
        Days=round(as.numeric(difftime(LastExit,FirstEntry, "days")),2)
        
     #select only the exits  
      FileIData=cSplit(FileIData, 'Type', sep=" ", type.convert=FALSE)
      FileIData=FileIData %>% filter(Type_1=="Entry")
      
      nEntries=nrow(FileIData)
      
     #Calcualte largest lost starting at initial capital, and count number of sequential lost entries
      colnames(FileIData)[6] <- "TradeProfit"
      colnames(FileIData)[1] <- "TradeNumber"
      Profit=FileIData[1,8]
      

     #cluster entries for martingales...this is place as S:1, S:2 etc...when no martainagle used is only S...
      nNcol=ncol(FileIData)
      FileIData=cSplit(FileIData, 'Signal', sep=":", type.convert=FALSE)
      SplitNCol=ncol(FileIData)
      
      FileIData$ClusterNum=0
      if (nNcol==SplitNCol){
      FileIData$ClusterNum=c(nrow(FileIData):1)} else {
          ClustCounter=0
          for (RawI in nrow(FileIData):1){
            if(FileIData$Signal_2[RawI]==1){ClustCounter=ClustCounter+1}
            FileIData$ClusterNum[RawI]=ClustCounter
          }
      } 

      #Checkif in cluster
      FileIData$IsCluster=FALSE
      IsCluster=FALSE
      for (RawI in nrow(FileIData):1){
        if(length(FileIData$ClusterNum[RawI-1])==0){if(FileIData$ClusterNum[RawI]==FileIData$ClusterNum[RawI+1]){FileIData$IsCluster[RawI]=TRUE};next} ## for top raw
        if(is.na(FileIData$ClusterNum[RawI+1])){if(FileIData$ClusterNum[RawI]==FileIData$ClusterNum[RawI-1]){FileIData$IsCluster[RawI]=TRUE};next} ## for Bottom raw
        if(FileIData$ClusterNum[RawI]==FileIData$ClusterNum[RawI-1] || FileIData$ClusterNum[RawI]==FileIData$ClusterNum[RawI+1]){FileIData$IsCluster[RawI]=TRUE}
      }
      
      
      #Checkif if consecutive lost
      FileIData$SequentialLost=0
      IsLost=0
      for (RawI in nrow(FileIData):1){
        if(is.na(FileIData$TradeProfit[RawI+1])){if(FileIData$TradeProfit[RawI]<=0 ){IsLost=IsLost+1};FileIData$SequentialLost[RawI]=IsLost;next}
        if(FileIData$TradeProfit[RawI]<=0 && FileIData$TradeProfit[RawI+1]>=0){IsLost=0}
        if(FileIData$TradeProfit[RawI]<=0 ){IsLost=IsLost+1}
        if(FileIData$TradeProfit[RawI]>=0 ){IsLost=0}
        FileIData$SequentialLost[RawI]=IsLost
      }
      
      
      
      
FileIData=FileIData[,c("TradeNumber", "CumProf","TradeProfit", "MoneyDD", "ClusterNum", "IsCluster", "SequentialLost")]
    
     #add calculate maximim drop in account equity starting at intial capital. Profile Account equity Capped at initial capital
      FileIData$LargestConsLost=0
      CumDD=0 #starting lost
      CumProf=0 #starting lost..variable contanins the cummulative profit each time the profit become positive...to assome we always start after taking the worse case scenario

      for (RawI in nrow(FileIData):1){ #it needs to start from the last raw raw (First  entry), which is the raw at the bottom in the list of entries.
        
        TradeIProfit=FileIData$TradeProfit[RawI]
        DD=-FileIData$MoneyDD[RawI] #dd is given as positive, but need to be turned into a lost, so we make it negative
        IsWinner=ifelse(TradeIProfit>=0, TRUE, FALSE)
        
        
        if(IsWinner==FALSE) {
          CumDD = CumDD+DD; 
          CumProf=CumProf+TradeIProfit
          FileIData$LargestConsLost[RawI]=CumDD

        } 
        
        
        if(IsWinner==TRUE)  {
          FileIData$LargestConsLost[RawI]=CumDD+DD
          if(FileIData$IsCluster[RawI]==TRUE){CumDD = CumDD+DD} else {CumDD = CumDD+TradeIProfit}
          
          CumProf=CumProf+TradeIProfit
          if(length(FileIData$ClusterNum[RawI-1])==0){next}
          if(CumProf>0){ if (FileIData$ClusterNum[RawI]!=FileIData$ClusterNum[RawI-1]){CumDD=0; CumProf=0}} ## reset only if the consequtntive trades are not part of a cluster
         
      }
    
    }  
      
      
      
      
      
      
      ##max number of consecutive losing entries
          nLossesClosing=max(FileIData$SequentialLost) # counts by method of closing all entries
          nLossesMart=FileIData %>% count(ClusterNum, sort = TRUE)
          nLossesMart=head(nLossesMart,1)$n
          nLostEntries=max(nLossesClosing,nLossesMart) #max number of lossing entries in a raw
 
      ##number of wining trades
          nWinTrades=sum(FileIData$TradeProfit >=0)
      
      ##Calcualte MAximum Cummulative D
      MaxDDMoney=min(FileIData$LargestConsLost)


      MaxDD=data.frame(MaxDDMoney, nLostEntries)
      
      MaxDDs=data.frame(gsub(".csv","", FileI),Profit,Days=Days,MaxDD,nEntries=nEntries, nWinTrades=nWinTrades)
      
      colnames(MaxDDs)=c("ID", "Profit","nDays", "MaxDDMoney",  "nLostEntries", "nEntries", "nWinTrades")
      
      Summary=rbind(Summary,MaxDDs)
      colnames(Summary)=c("ID", "Profit","nDays","MaxDDMoney",  "nLostEntries",  "nEntries", "nWinTrades")
    }
    
   

##add percent DD
    Summary$PercDD=round(Summary$MaxDDMoney/StartingBalance*100,1)
   

#############################################################################
#############--------summary results of all pairs-----------#################
#############################################################################
   

    SummaryResults=data.frame()
    SummaryFiles=ListEntries[grep("Optimora_", x = ListEntries$FileName),]$FileName
    
    IsOptiMora=ifelse(length(SummaryFiles)==0,FALSE,TRUE) #collect data differently if usuing old otpimizer
    if (IsOptiMora==FALSE){SummaryFiles=ListEntries[grep(paste(Pairs,collapse="|"), x = ListEntries$FileName),]$FileName}
    
    
    for (SummaryFileI in SummaryFiles){

      SummaryFileIData=read.csv(paste0(Path,SummaryFileI)) #,sep=";"
      
      #if files has less than five row it means it dod not load correcly due to the use of semicolon instead of  a comma
      if(ncol(SummaryFileIData)< 5){
      SummaryFileIData=read.csv(paste0(Path,SummaryFileI),sep=";") 
      }
      
      #remove unnecesary columns if sumamry file is from old optimizer
      if(IsOptiMora==FALSE){
          PairName=substring(SummaryFileI,1,6) 
          #get first column of parameters of bot
          FirtCol=grep("X__Name.for.robot",colnames(SummaryFileIData))
          SummaryFileIData[2:(FirtCol-1)]=NULL #do not delete the first columns whithc is the name of the list of entrie

          #there is a variant among coputers, in which the comment field appears last, in others appears earlier.
          LastColName=colnames(SummaryFileIData)[ncol(SummaryFileIData)]
          if(LastColName=="comment"){SummaryFileIData[ncol(SummaryFileIData)]=NULL} 
          SummaryFileIData$Ticker=PairName
      }
      
      #get defaults parameters (keep record for later use)
      Ncols=ncol(SummaryFileIData)
        DefaultPars=SummaryFileIData[1,c(1,1:(Ncols-2))] #last two columns are not parameters for the bot
        DefaultPars=t(DefaultPars) #tranvert to better display in rows...
        DefaultPars=cbind(rownames(DefaultPars),DefaultPars)
        colnames(DefaultPars)=c("Parameter", "Value")
        DefaultPars=as.data.frame(DefaultPars)
        rownames(DefaultPars)<-NULL
        DefaultPars=DefaultPars[-(1:2),] #delete the ID raws
        
      #get the two parameters optmized
        
        OptiPars=SummaryFileIData[-1, ] #delete the first raw, which contains the dafault parameters. 
        OptiPars[OptiPars == ''] <- NA
        OptiPars[OptiPars == ' '] <- NA
        OptiPars=OptiPars[ , colSums(is.na(OptiPars)) == 0]
      
        SummaryResults=rbind(SummaryResults,OptiPars)
    }
    
    XName=colnames(SummaryResults)[2]
    YName=colnames(SummaryResults)[3]
    if(IsOptiMora==FALSE){colnames(SummaryResults)=c("ID", "X", "Y",  "Pair")} else {colnames(SummaryResults)=c("ID", "X", "Y",  "Profit", "Pair"); SummaryResults$Profit=NULL } #profit is taken from the list of entries, instead
    SummaryResults=data.frame(lapply(SummaryResults, function(x) {gsub("run\\", "", x, fixed=TRUE)})) 
    SummaryResults=data.frame(lapply(SummaryResults, function(x) {gsub(".csv", "", x)})) 
   


    
    
    #allresults of profit and DD
    FullResults=merge(Summary,SummaryResults, by="ID")
    
    #Replace time frames for minutes to allow sorting in plot
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("1 minute", "1", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("3 minutes", "3", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("5 minutes", "5", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("15 minutes", "15", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("30 minutes", "30", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("45 minutes", "45", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("1 hour", "60", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("2 hours", "120", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("3 hours", "180", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("4 hours", "240", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("1 day", "1440", x)})) #remove minutes..to allow later the sorting
      FullResults <- data.frame(lapply(FullResults, function(x) {gsub("1 week", "10080", x)})) #remove minutes..to allow later the sorting
       

    #Convert columsn to numeric...the ones that can
      numeric_cols <- data.frame(sapply(FullResults, Hmisc::all.is.numeric))#convert columns to numeric...find out if column can be converted to numeric
      colnames(numeric_cols)="IsNUmeric"
      numeric_cols$Var=rownames(numeric_cols)
      numeric_cols=numeric_cols %>% filter(IsNUmeric==TRUE) #select all  varibales that can be conterd
      NumericColumns=numeric_cols$Var #list of convertable variables
    
    FullResults[, NumericColumns] <- lapply(NumericColumns, function(x) as.numeric(FullResults[[x]])) #converts them to numeric
    FullResults$MaxDDMoney=-1*(FullResults$MaxDDMoney)

    FullResults$DDAccount=FullResults$MaxDDMoney/StartingBalance*100 # DD as percent of initical equity
    FullResults$DD3Perc= (DesireMaxDD/FullResults$DDAccount)*100 #Percent of account to enter..standarized to have % drowdown of all account euitey 
    FullResults$MoneyEntryAdjusted= (FullResults$DD3Perc/100)*StartingBalance #Percent of account to enter..standarized to have % drowdown of all account euitey 
    FullResults$ProfitAt3Perc=FullResults$Profit*(FullResults$DD3Perc /100) #profit shall we enter with enough money to cause a %DD
    FullResults$ProfitStan3PercDay=FullResults$ProfitAt3Perc/FullResults$nDays
    FullResults$PercentDaysActive=FullResults$nEntries/FullResults$nDays
    
    FullResults$FailByAmount=ifelse(FullResults$MoneyEntryAdjusted<=MinMoneyEntry,"Yes","No")
    FullResults$FailByTimeActive=ifelse(FullResults$PercentDaysActive<=MinActive,"Yes","No")
    
    FullResults$MeetTarget=ifelse(FullResults$ProfitStan3PercDay >=GainAtTarget,"Yes","No")
    
    LimVals=range(FullResults$ProfitStan3PercDay) #used for colorscale in plot of all pairs
    LimVals=max(abs(LimVals))
    #Calculate account summary
    Filtered= FullResults %>% mutate(ProfitStan3PercDay=ifelse(FailByAmount=="Yes"  | FailByTimeActive=="Yes", 0, ProfitStan3PercDay)) #set profit to zero for pairs that do not meet criteria
    

    #count number of pairs that reach 1% profit per day target
      MeetTarget=Filtered
      
      MeetTarget=MeetTarget %>% mutate(MeetProf = ifelse(ProfitStan3PercDay >=GainAtTarget,1,0)) %>% group_by(X,Y) %>% summarise(nOnTarget = sum(MeetProf))

      MeetTarget=data.frame(as.data.table(MeetTarget))
      MeetTarget$X=factor(MeetTarget$X)
      MeetTarget$Y=factor(MeetTarget$Y)
    
       MeetTargetPlot= ggplot(MeetTarget, aes(X,Y, fill= nOnTarget )) + 
        geom_tile(stat="identity") + 
        labs(x=XName, y=YName)+
        theme_bw()+
        coord_cartesian(expand = FALSE)+
        scale_fill_gradient(low =  "white", high = "blue", name="", limits = c(0, 10))+
        #scale_fill_fermenter(palette = "Blues",direction=1, name="")+
        theme(panel.grid=element_blank(),panel.border = element_rect(color = "black"))

        MeetTargetPlot=ggplotly(MeetTargetPlot)
    
    

    #summary results of complete account (entering in all pairs) with the results of each pair
    Passing <-  Filtered %>% group_by(X,Y)%>% summarize(AccProf = sum(ProfitStan3PercDay))
    colnames(Passing)=c("X","Y", "ProfitStan3PercDay")
    All=Passing$ProfitStan3PercDay
    
    Passing =data.frame(as.data.table(Passing ))
      #find most profitable parameters
          Best=Passing[which.max(Passing$ProfitStan3PercDay), ] # most profitable parameters
          BestX=Best$X
          BestY=Best$Y
      #Results of best parameter...to be used in robot
          BestPar=FullResults[FullResults[,"X"]==BestX & FullResults[,"Y"]==BestY,]
          BestPar <- BestPar[order(BestPar$ProfitStan3PercDay , decreasing =TRUE), ]
    

    
    #Plot for summary of account
    Passing $X=factor(Passing $X)
    Passing $Y=factor(Passing $Y)
    Limit=max(abs(max(Passing$ProfitStan3PercDay, na.rm=TRUE)), abs (min(Passing$ProfitStan3PercDay, na.rm=TRUE)))
    #Doplot
     Raster= ggplot(Passing, aes(X,Y, fill= ProfitStan3PercDay )) + 
          geom_tile(stat="identity") + 
          labs(x=XName, y=YName)+
          theme_bw()+
          coord_cartesian(expand = FALSE)+
          scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0,  name="", limits = c(-Limit, Limit))+
          #scale_fill_fermenter(palette = "Blues",direction=1, name="")+
          theme(panel.grid=element_blank(),panel.border = element_rect(color = "black"))
  
      Raster=ggplotly(Raster)
   
   
    
    
#Plot capped profits at target profit PLOT capping standarized profit to tartget of 1%...this is to avoid the effect of pairs that make too much, biasing summary results
    CappedPair=data.frame(as.data.table(Filtered))
    CappedPair$PCapped=ifelse(CappedPair$ProfitStan3PercDay >=GainAtTarget,GainAtTarget,CappedPair$ProfitStan3PercDay)
    CappedPair=CappedPair %>%  group_by(X,Y) %>% summarise(Balance = sum(PCapped))   
  
    All=data.frame(RawPassProfit=All, CappedProfit=CappedPair$Balance)
      CappedPair$X=factor(CappedPair$X)
      CappedPair$Y=factor(CappedPair$Y)
      LimitCap=max(abs(max(CappedPair$Balance, na.rm=TRUE)), abs (min(CappedPair$Balance, na.rm=TRUE)))
      CappedPairPlot= ggplot(CappedPair, aes(X,Y, fill= Balance )) + 
            geom_tile(stat="identity") + 
            labs(x=XName, y=YName)+
            theme_bw()+
            coord_cartesian(expand = FALSE)+
            scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0,  name="", limits = c(-LimitCap, LimitCap))+
            #scale_fill_fermenter(palette = "Blues",direction=1, name="")+
            theme(panel.grid=element_blank(),panel.border = element_rect(color = "black"))

    CappedPairPlot=ggplotly(CappedPairPlot)
    
    
    
   #BarPlo
   BestPar$ID=NULL
  BarPlot= ggplot(BestPar, aes(x=reorder(Pair, -ProfitStan3PercDay)    , y=ProfitStan3PercDay ,fill=ProfitStan3PercDay )) + 
    labs(title="",x="", y="Profit per day standarized to a desired dropdown")+
    geom_bar(stat="identity", width=0.5)+
    scale_fill_gradient2(low = "red", mid = "lightgrey", high = "blue", name="", limits = c(-Limit, Limit))+
    theme_bw()
  
 BarPlot=BarPlot + theme(axis.text.x=element_text(color = "black",  angle=90))
 BarPlot=BarPlot  + geom_hline(yintercept=GainAtTarget, linetype="dashed", color = "red",size=0.5)

  BarPlot=ggplotly(BarPlot,tooltip="y")
  


   #Save profits of best parameters
  FileName=paste0(NameOptimization,".csv")
  write.csv(All,FileName)
    
```


$$\\[.0005in]$$
**PARAMETERS OPTIMIZED** <br />
``r  XName ``  and ``r  YName ``<br /><br />

**BEST PARAMETERS** <br />
``r  XName `` = ``r  BestX `` <br />
``r  YName `` = ``r  BestY `` <br />
Profit account=  ``r  round(sum(BestPar$ProfitStan3PercDay ),0) `` (per day adjusted to desire% DD ) <br />
Activity = ``r  round(sum(BestPar$nEntries )/max(BestPar$nDays ),2) `` (Cumulative number of entries in all pairs per week)<br />
Desire DD = ``r DesireMaxDD``

$$\\[.0005in]$$
<center>
<span style="color: red;">**Profit per day standardized to the desire percent dropdown**</span><br />
Exclude pairs that when standardized to DD enter with less than $1,000 and pairs that fail to enter once a week

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
Raster
```


<br /><br />

<span style="color: red;">**Capping pairs profit per day standardized to a desire percent dropdown**</span><br />
The figure below is like the one above but capping the profits of all pairs to a traget of 1%, this avoids biasing the summary results of an account when only a handful of pairs yield very large profits. This figure basically trying to provide a sense of the extent to which the strategy is profitable across pairs.

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
CappedPairPlot
```


<br /><br />

Comparison to prior optimizations of this robot. Double click on the plot to deselect all columns.

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
FilePath=dirname(rstudioapi::getSourceEditorContext()$path)
FilesPriorBot=  data.frame(FileName=list.files(paste0(FilePath,"/")))
FilesPriorBot=data.frame(FileName=FilesPriorBot[grep(RobotName, x = FilesPriorBot$FileName),])
FilesPriorBot=data.frame(FileName=FilesPriorBot[grep("csv", x = FilesPriorBot$FileName),])
FilesPriorBot=data.frame(FileName=FilesPriorBot[grep("BestPerpair", x = FilesPriorBot$FileName, invert=TRUE),])$FileName

Optimizations=data.frame()
for (FileIinBot in FilesPriorBot){
  OptimizationName=gsub(".csv","",FileIinBot)
  ResultOptimizationI= read.csv(paste0(FilePath,"/",FileIinBot)) 
  ResultOptimizationI$Name=OptimizationName
  Optimizations=rbind(Optimizations,ResultOptimizationI)
}

#remove optimizations with zeros
Optimizations=Optimizations %>% filter(CappedProfit>0)

Optimizations=Optimizations[order(Optimizations$CappedProfit, decreasing = TRUE), ] 
Optimizations$X=1:nrow(Optimizations)
Labels=Optimizations$Name


#do bar plot
OptiComparison=ggplot(Optimizations, aes(X, CappedProfit)) +
    labs(title="",x="Rank", y="Capped Profit")+
   theme_bw()+
    geom_col(mapping = aes(fill = Name),  position = position_dodge()) +
  #  scale_fill_manual("legend", values = color)
#    scale_alpha_manual(values = c(1))+
    theme(legend.title = element_blank())

    OptiComparison=ggplotly(OptiComparison,tooltip="Name")
  
OptiComparison



```

<br /><br />


Number of pairs that meet 1% profit target

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
MeetTargetPlot
```

<br /><br />
Results for ``r  XName `` = ``r  BestX ``  and ``r  YName `` = ``r  BestY ``<br /><br />






```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
BarPlot
```
</center>


<details>
  <summary>Best parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(BestPar)
```
</details> 



<center>

**Results by pair**
```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}
library(RColorBrewer)  #Also offer more options

FullResults$X=factor(FullResults$X)
FullResults$Y=factor(FullResults$Y)
      
Blues=colorRampPalette(brewer.pal(9,"GnBu"))
Reds=colorRampPalette(brewer.pal(9,"OrRd"))

   Pairs= ggplot(FullResults, aes(X,Y, fill= ProfitStan3PercDay )) + 
        geom_tile(stat="identity")+
        labs(x=XName, y=YName)+
        theme_bw()+
        coord_cartesian(expand = FALSE)+
        scale_fill_gradientn( colors=c( rev(Reds(9)), "white", (Blues(9)) ), limits = c(-LimVals, LimVals),  name="")+
        facet_wrap(~ Pair)+
        theme(axis.text = element_text( size = 5),panel.spacing.x=unit(0.5, "lines") , panel.spacing.y=unit(1,"lines"))

Pairs=ggplotly(Pairs) 

#Pairs=Pairs%>% layout(margin = list( l = 1, b=1))

#Results capped
Pairs

```


$$\\[.005in]$$
</center>




<center>

**Results by pair capped to desired 1% profit** </br>
This is the same as above, but caps pairs to max desire profit to avoid visual bias by pairs with very lage profits

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}

PairCapped= FullResults %>% mutate(ProfitStan3PercDay  = ifelse(ProfitStan3PercDay  >=GainAtTarget,GainAtTarget,ProfitStan3PercDay )) #set profit to zero for pairs that do not meet criteria
   PairCappedPlot= ggplot(PairCapped, aes(X,Y, fill= ProfitStan3PercDay )) + 
        geom_tile(stat="identity")+
        facet_wrap(~ Pair)+
        labs(x=XName, y=YName)+
        theme_bw()+
        coord_cartesian(expand = FALSE)+
        scale_fill_gradientn( colors=c( rev(Reds(9)), "white", (Blues(9)) ), limits = c(-GainAtTarget, GainAtTarget),  name="")+

        theme(axis.text = element_text( size = 5),panel.spacing.x=unit(0.1, "lines") ,panel.spacing.y=unit(1,"lines"))

PairCappedPlot=ggplotly(PairCappedPlot) 

#Pairs=Pairs%>% layout(margin = list( l = 1, b=1))

#Results capped
PairCappedPlot

```


$$\\[.005in]$$
</center>



    
    


<center>

**Results within desire DD, top 5 with most winning trades, and ranked by Profit per day at desire DD** </br>
One is in the search of a unique combination of parameters that can be used across forex pairs; the reality is, however, that they represent countries with vast differences in economic power, which can cause specific patterns within certain pairs, thus, in most likelihoods parameters are specific to each forex pair. Here I show the best results for each pair.

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center'}

#select desire combinations only
BestPerPair=FullResults %>% filter(PercDD>=-DesireMaxDD)
BestPerPair=BestPerPair %>% group_by(Pair) %>% slice_max(order_by = nWinTrades, n = 5)
BestPerPair$YName=YName
BestPerPair$XName=XName
  NameX=paste0(NameOptimization,"_BestPerpair.csv")
  write.csv(BestPerPair,NameX)
  

PastBestPerPairFile=  data.frame(FileName=list.files(paste0(FilePath,"/")))
PastBestPerPairFile=data.frame(FileName=PastBestPerPairFile[grep(RobotName, x = PastBestPerPairFile$FileName),])
PastBestPerPairFile=data.frame(FileName=PastBestPerPairFile[grep("csv", x = PastBestPerPairFile$FileName),])
PastBestPerPairFile=data.frame(FileName=PastBestPerPairFile[grep("BestPerpair", x = PastBestPerPairFile$FileName),])$FileName

PairsBests=data.frame()
for (FileIinBot in PastBestPerPairFile){
  OptimizationName=gsub("_BestPerpair.csv","",FileIinBot)
  ResultOptimizationI= read.csv(paste0(FilePath,"/",FileIinBot)) 
  ResultOptimizationI$Name=OptimizationName
  PairsBests=rbind(PairsBests,ResultOptimizationI)
}

#cap extreme values to maxmium  desire profit
Cap=StartingBalance*(MaxDesDayProf/100)
 
PairsBests$PCapped=ifelse(PairsBests$ProfitStan3PercDay >=Cap,Cap,PairsBests$ProfitStan3PercDay)
PairsBests=PairsBests[with(PairsBests, order(Pair, -PCapped)),]

PairsBests=PairsBests %>% group_by(Pair) %>% mutate(Xaxis = 1:n())

PairsBests=data.frame(PairsBests)

ToolTip=paste(PairsBests$Name,
              '<br>',PairsBests$YName, ": ", PairsBests$Y,
              '<br>',PairsBests$XName, ": ", PairsBests$X)



#do bar plot
OptiComparison=ggplot(PairsBests, aes(Xaxis, PCapped, text = ToolTip)) +
    labs(title="",x="", y="Capped Profit")+
   theme_bw()+
          facet_wrap(~ Pair)+
    geom_col(mapping = aes(fill = Name),  position = position_dodge()) +

    theme(legend.title = element_blank(), axis.text.x=element_blank())

    OptiComparison=ggplotly(OptiComparison,tooltip="ToolTip")
  
OptiComparison


```


$$\\[.005in]$$
</center>

    
    
    
    
    
    
    
    
<details>
  <summary>Default parameters</summary>
```{r, echo=FALSE, eval=TRUE}
knitr::kable(DefaultPars)
```
</details> 
